---
title: "Loading data"
output: html_notebook
---

# Part 0: Customise functions
```{r}
standardise <- function(x) {
  # Standardize x
  standardized_x <- ((x - mean(x)) / sd(x))
  
  # Return the standardized vector
  return(standardized_x)
}

standardize_dataframe <- function(data) {
  # Apply standardization to all numeric columns in the dataframe
  data_standardised <- as.data.frame(lapply(data, function(x) {
    if(is.numeric(x)) {
      return(standardise(x))
    } else {
      return(x)
    }
  }))
  
  # Return the standardized dataframe
  return(data_standardised)
}

```

# Part 1: Load data from .xlsx file
```{r}
library(readxl)

data_real <- read_excel("./data/20240418_data_in.xlsx")
str(data_real)

data_real_s <- standardize_dataframe(data_real)
str(data_real_s)
```

# Part 2: Create some simulated non-sense data for testing of the model

## a. For Teaching -> Overall <- CourseStruc
```{r}
n <- 100
Teaching <- rnorm(n, 0, 0.5)
CourseStruc <- rnorm(n, 0.75*3 + 0.25*Teaching, 0.5)
Overall <- rnorm(n, 0.2*5 + 0.6 * Teaching + 0.2*CourseStruc, 0.2)

data_sim <- data.frame(Teaching, CourseStruc, Overall)

data_sim_s <- standardize_dataframe(data_sim)
str(data_sim_s)

```

## b. Return Rate -> Overall Impression
```{r}
n <- 100
ReturnRate <- rnorm(n, 0.3, 0.1)
Overall <- rnorm(n, 0.8*5 + 0.2 * ReturnRate, 0.2)

data_sim <- data.frame(ReturnRate, Overall)

data_sim_s <- standardize_dataframe(data_sim)
str(data_sim_s)

plot(data_sim$Overall, data_sim$ReturnRate, col="green")
points(data_real$Overall, data_real$Percentage, col="purple")
```

# Part 3: Prior predictive simulation

## a. For Teaching -> Overall
```{r}
library(rethinking)

n <- 100
a <- rnorm(n, 0, 1)
b_T <- rnorm(n, 1, 0.5)

plot(NULL, xlim = c(1, 5), ylim = c(1, 5),
xlab = "Teaching",
ylab = "Overall Impression")
Aseq <- seq(from = -1, to = 6, len = 50)
for (i in 1:n) {
    mu <- a[i] + b_T[i] * Aseq
    lines(Aseq, mu, lwd = 0.5, col = "blue")
}
points(data_real$Teaching,data_real$Overall,col="green", cex=1.5, pch=19)
```

## b. For Teaching -> Course Structure
```{r}
library(rethinking)

n <- 100
a <- rnorm(n, 0.1, 1)
b_TC <- rnorm(n, 0.5, 1)

plot(NULL, xlim = c(1, 5), ylim = c(1, 5),
xlab = "Course Structure",
ylab = "Teaching")
Aseq <- seq(from = -1, to = 6, len = 50)
for (i in 1:n) {
    mu <- a[i] + b_TC[i] * Aseq
    lines(Aseq, mu, lwd = 0.5, col = "blue")
}
points(data_real$CourseStruc,data_real$Teaching,col="red", cex=1.5, pch=19)
```

## c. For Course Structure -> Overall Impression
```{r}
library(rethinking)

n <- 100
a <- rnorm(n, 0.1, 1)
b_C <- rnorm(n, 0.5, 1)

plot(NULL, xlim = c(1, 5), ylim = c(1, 5),
xlab = "Overall Impression",
ylab = "Course Structure")
Aseq <- seq(from = -1, to = 6, len = 50)
for (i in 1:n) {
    mu <- a[i] + b_C[i] * Aseq
    lines(Aseq, mu, lwd = 0.5, col = "blue")
}
points(data_real$Overall,data_real$CourseStruc,col="yellow", cex=1.5, pch=19)
```

## d. For return_rate -> Overall
```{r}
library(rethinking)

n <- 100
a <- rnorm(n, 3, 1)
b_rr <- rnorm(n, 1, 1)

plot(NULL, xlim = c(0, 1), ylim = c(0, 6),
xlab = "Return Rate",
ylab = "Overall Impression")
Aseq <- seq(from = -10, to = 10, len = 50)
for (i in 1:n) {
    mu <- a[i] + b_rr[i] * Aseq
    lines(Aseq, mu, lwd = 0.5, col = "green")
}
points(data_real$Percentage,data_real$Overall,col="purple", cex=1.5, pch=19)
```

# Part 4: Build prediction models

## a. Teaching -> Overall
```{r}
# Choose between simulated and real data
data_in <- data_real

# Define the input data
dlist <- list(
    Teaching = data_in$Teaching,
    Structure = data_in$CourseStruc,
    Overall = data_in$Overall
)

model_m1 <- ulam(
    alist(
    # CourseStruc -> Overall model
    Overall ~ dnorm(mu, sigma),
    mu <- a + b_T * Teaching,
    a ~ dnorm(0, 1),
    b_T ~ dnorm(0, 0.2),
    sigma ~ dexp(1)
    ), data = dlist
)
```

## b. CourseStruc -> Overall <- Teaching with interaction Teaching -> Course Struc
```{r}
# Choose between simulated and real data
data_in <- data_sim

# Define the input data
dlist <- list(
    Teaching = data_in$Teaching,
    Structure = data_in$CourseStruc,
    Overall = data_in$Overall
)

model_m4 <- ulam(
    alist(
    # CourseStruc -> Overall <- Teaching
    Overall ~ dnorm(mu, sigma),
    mu <- a + b_T * Teaching + b_C * Structure,
    a ~ dnorm(0.1, 1),
    b_T ~ dnorm(1, 1),
    b_C ~ dnorm(0.5, 1),
    sigma ~ dexp(1),

    # Teaching -> CourseStruc
    Structure ~ dnorm(nu, tau),
    nu <- a_T + b_CT * Teaching,
    a_T ~ dnorm(0, 1),
    b_CT ~ dnorm(0.5, 1),
    tau ~ dexp(1)
    ), data = dlist, chains = 2, cores = 2
)
```

## c. Return Rate -> Overall Impression
```{r}
# Choose between simulated and real data
data_in <- data_sim

# Define the input data
dlist <- list(
    ReturnRate = data_in$Percentage,
    Teaching = data_in$Teaching,
    Structure = data_in$CourseStruc,
    Overall = data_in$Overall
)

model_m4 <- ulam(
    alist(
    # CourseStruc -> Overall <- Teaching
    Overall ~ dnorm(mu, sigma),
    mu <- a + b_rr * ReturnRate,
    a ~ dnorm(3, 1),
    b_rr ~ dnorm(1, 1)
    sigma ~ dexp(1)

    ), data = dlist, chains = 2, cores = 2
)
```