# Data loading and preparing

# Load libraries
```{r}
library(dplyr)
library(corrplot)
library(ggplot2)
library(svglite)
library(rethinking)
```

# Load raw data frame and convert to integer and numeric
```{r}
load("./data/data_r_in.RData")
d_in <- data_in
d_in_s <- data_in

d_in$Swedish <- as.integer(d_in$Swedish) + 1
d_in$CS <- as.integer(d_in$CS) + 1
d_in$Survey_population <- as.numeric(d_in$Survey_population)
d_in$Survey_returned <- as.numeric(d_in$Survey_returned)
d_in$year <- as.integer(d_in$year)
d_in$study_period <- as.integer(d_in$study_period)

d_in$Percentage <- as.numeric(d_in$Percentage)
d_in_s$Percentage <- standardize(d_in$Percentage)
d_in$Overall <- as.numeric(d_in$Overall)
d_in_s$Overall <- standardize(d_in$Overall)
d_in$Prerequisites <- as.numeric(d_in$Prerequisites)
d_in_s$Prerequisites <- standardize(d_in$Prerequisites)
d_in$LearningOutcome <- as.numeric(d_in$LearningOutcome)
d_in_s$LearningOutcome <- standardize(d_in$LearningOutcome)
d_in$CourseStruc <- as.numeric(d_in$CourseStruc)
d_in_s$CourseStruc <- standardize(d_in$CourseStruc)
d_in$Teaching <- as.numeric(d_in$Teaching)
d_in_s$Teaching <- standardize(d_in$Teaching)
d_in$Literature <- as.numeric(d_in$Literature)
d_in_s$Literature <- standardize(d_in$Literature)
d_in$Assessment <- as.numeric(d_in$Assessment)
d_in_s$Assessment <- standardize(d_in$Assessment)
d_in$Admin <- as.numeric(d_in$Admin)
d_in_s$Admin <- standardize(d_in$Admin)
d_in$Workload <- as.numeric(d_in$Workload)
d_in_s$Workload <- standardize(d_in$Workload)
d_in$Equality <- as.numeric(d_in$Equality)
d_in_s$Equality <- standardize(d_in$Equality)

save(d_in, d_in_s, file = "./data/data_r_in_num")
```

# Exploring correlations in data
```{r}
dlist <- list(
      
      Size = as.integer(d_in$Survey_population),
      Swedish = as.integer(d_in$Swedish),
      Overall_s = standardize(as.numeric(d_in$Overall)),
      Prereq_s = standardize(as.numeric(d_in$Prerequisites)),
      LearningOut_s = standardize(as.numeric(d_in$LearningOutcome)),
      Structure_s = standardize(as.numeric(d_in$CourseStruc)),
      Teaching_s = standardize(as.numeric(d_in$Teaching)),
      Literature_s = standardize(as.numeric(d_in$Literature)),
      Assessment_s = standardize(as.numeric(d_in$Assessment)),
      Admin_s = standardize(as.numeric(d_in$Admin)),
      Workload_s = standardize(as.numeric(d_in$Workload)),
      Equality_s = standardize(as.numeric(d_in$Equality))
)
```

```{r}
model_m1 <- ulam(log_lik=TRUE,
      alist(
      Overall_s ~ dnorm(mu, sigma),
      mu <- a[Swedish] + b_p * Prereq_s + b_l * LearningOut_s + b_s * Structure_s + b_t * Teaching_s + b_li * Literature_s + b_a * Assessment_s + b_ad * Admin_s + b_w * Workload_s + b_e * Equality_s,
      a[Swedish] ~ dnorm(0, 1),
      b_p ~ dnorm(0, 1),
      b_l ~ dnorm(0, 1),
      b_s ~ dnorm(0, 1),
      b_t ~ dnorm(0, 1),
      b_li ~ dnorm(0, 1),
      b_a ~ dnorm(0, 1),
      b_ad ~ dnorm(0, 1),
      b_w ~ dnorm(0, 1),
      b_e ~ dnorm(0, 1),
      sigma ~ dexp(1)
      ), data = dlist, chains = 2, cores = 2

)
```

```{r}
model_mrq1a <- ulam(log_lik=TRUE,
      alist(
      Workload_s ~ dnorm(mu, sigma),
      mu <- a_0 + b_p * Prereq_s + b_l * LearningOut_s + b_s * Structure_s + b_t * Teaching_s + b_li * Literature_s + b_a * Assessment_s + b_ad * Admin_s + b_e * Equality_s,
      a_0 ~ dnorm(0, 1),
      b_p ~ dnorm(0, 1),
      b_l ~ dnorm(0, 1),
      b_s ~ dnorm(0, 1),
      b_t ~ dnorm(0, 1),
      b_li ~ dnorm(0, 1),
      b_a ~ dnorm(0, 1),
      b_ad ~ dnorm(0, 1),
      b_e ~ dnorm(0, 1),
      sigma ~ dexp(1)
      ), data = dlist, chains = 2, cores = 2

)
```

```{r}
model_mrq1b <- ulam(log_lik=TRUE,
      alist(
      Workload_s ~ dnorm(mu, sigma),
      mu <- a_0 + b_p * Prereq_s + b_l * LearningOut_s + b_s * Structure_s + b_t * Teaching_s + b_li * Literature_s + b_a * Assessment_s + b_ad * Admin_s + b_e * Equality_s,
      a_0 ~ dnorm(0, 1),
      b_p ~ dnorm(0, 1),
      b_l ~ dnorm(0, 1),
      b_s ~ dnorm(0, 1),
      b_t ~ dnorm(0, 1),
      b_li ~ dnorm(0, 1),
      b_a ~ dnorm(0, 1),
      b_ad ~ dnorm(0, 1),
      b_e ~ dnorm(0, 1),
      sigma ~ dexp(1),

      # Quality of Teaching influenced by other teaching related factors
      Teaching_s ~ dnorm(nu, tau),
      nu <- a_T + b_l_t * LearningOut_s + b_s_t * Structure_s + b_li_t * Literature_s + b_a_t * Assessment_s + b_ad_t * Admin_s + b_e_t * Equality_s,
      a_T ~ dnorm(0, 1),
      b_l_t ~ dnorm(0, 1),
      b_s_t ~ dnorm(0, 1),
      b_li_t ~ dnorm(0, 1),
      b_a_t ~ dnorm(0, 1),
      b_ad_t ~ dnorm(0, 1),
      b_e_t ~ dnorm(0, 1),
      tau ~ dexp(1)
      ), data = dlist, chains = 2, cores = 2

)
```

```{r}
model_mrq1c <- ulam(log_lik=TRUE,
      alist(
      Workload_s ~ dnorm(mu, sigma),
      mu <- a_0 + b_p * Prereq_s + b_l * LearningOut_s + b_s * Structure_s + b_t * Teaching_s + b_li * Literature_s + b_a * Assessment_s + b_ad * Admin_s + b_e * Equality_s + b_o * Overall_s,
      a_0 ~ dnorm(0, 1),
      b_p ~ dnorm(0, 1),
      b_l ~ dnorm(0, 1),
      b_s ~ dnorm(0, 1),
      b_t ~ dnorm(0, 1),
      b_li ~ dnorm(0, 1),
      b_a ~ dnorm(0, 1),
      b_ad ~ dnorm(0, 1),
      b_e ~ dnorm(0, 1),
      b_o ~ dnorm(0, 1),
      sigma ~ dexp(1),

      # Overall impression is related to everything
      Overall_s ~ dnorm(nu, tau),
      nu <- a_o + b_p_o * Prereq_s + b_l_o * LearningOut_s + b_s_o * Structure_s + b_t_o * Teaching_s + b_li_o * Literature_s + b_a_o * Assessment_s + b_ad_o * Admin_s + b_e_o * Equality_s,
      a_o ~ dnorm(0, 1),
      b_p_o ~ dnorm(0, 1),
      b_l_o ~ dnorm(0, 1),
      b_s_o ~ dnorm(0, 1),
      b_t_o ~ dnorm(0, 1),
      b_li_o ~ dnorm(0, 1),
      b_a_o ~ dnorm(0, 1),
      b_ad_o ~ dnorm(0, 1),
      b_e_o ~ dnorm(0, 1),
      tau ~ dexp(1)
      ), data = dlist, chains = 2, cores = 2

)
```

model_m2 <- ulam(log_lik=TRUE,
    alist(
    # T_S -> C_MW model 
    C_MW ~ dnorm(mu, sigma),
    mu <- a_C + b_C_T * T_S_std,
    a_C ~ dnorm(0, 1),
    b_C_T ~ dnorm(0.5, 0.5),
    sigma ~ dexp(1),

    # Sol -> T_S model
    T_S_std ~ dnorm(nu, tau),
    nu <- a_T + b_T_S * Sol_std,
    a_T ~ dnorm(0.5, 1),
    b_T_S ~ dnorm(0.5, 0.5),
    tau ~ dexp(1)
    ), data = dlist, chains = 2, cores = 2
)

```

```{r}
d_corr <- subset(d_in_s, select = -c(Swedish, CS, Course, year, study_period))

correlations <- cor(d_corr)
print(correlations)

svg("correlation_plot.svg", width = 10, height = 8)
corrplot(correlations, method = "pie")

dev.off()
```